% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.

\title{resume Deedy}
\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4
%\hyphenpenalty=1000
%\tolerance=1000

\newcommand{\skill}[1]{\runsubsection{#1}}
\newcommand{\distribute}[2]{#1\hfill #2 \hspace*{\fill}}

\begin{document}


\lastupdated % Print the Last Updated text at the top right

\namesection{Daniel}{Smith}{
\href{http://X1011.com}{X1011.com} \\ % Your website, LinkedIn profile or other web address
 % Your contact information
}


\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page


\section{Education} 
	
	\subsection{University of Texas at Dallas}
		\subtitle{BS in Computer Science}
		\detail{May 2011}
		\distribute {GPA: 3.806} {major GPA: 3.833} \\
		\begin{tightitemize}
			\item Computer Science honors\\
			\item Collegium V honors\\
			\item Academic Distinction full-tuition scholarship\\
		\end{tightitemize}
	\sectionspace
	
	\subsection{FUBiS}
		\subtitle{Free University of Berlin international summer program}
		\detail{August 2010}
		completed level B2 German course
	\sectionspace
	
	\subsection{Parkway West Career and Technology Center}
		\subtitle{Certificate in Computer Technology}
		\detail{\distribute {June 2007} {Pittsburgh, PA}  }
	\sectionspace


\section{Coursework}

\subsection{Graduate}

Advanced Machine Learning \\
Open Source Software Engineering \\
Advanced Interactive Graphics \\
Compilers + Practicum \\
Cloud Computing

\sectionspace


\subsection{Undergraduate}

Information Retrieval \\
Operating Systems \\
Artificial Intelligence + Practicum \\
Functional Programming \\
Computer Graphics + Practicum \\
{\footnotesize \textit{\textbf{(Research Asst. \& Teaching Asst) }}} \\
Unix Tools and Scripting

\sectionspace


\end{minipage} % The end of the left column
\hfill
%
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page


\section{Skills}
\skill{} 


\sectionspace


\section{Experience}

\runsubsection{Coursera}
\subtitle{| KPCB Fellow + Software Engineering Intern}

\detail{Expected June 2014 – Sep 2014 | Mountain View, CA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item 52 out of 2500 applicants chosen to be a KPCB Fellow 2014.
\end{tightitemize}

\sectionspace


\runsubsection{Google}
\subtitle{| Software Engineering Intern}

\detail{May 2013 – Aug 2013 | Mountain View, CA}
\begin{tightitemize}
\item Worked on the YouTube Captions team in primarily vanilla Javascript and Python to plan, design and develop the full stack implementation of a new framework to add and edit Automatic Speech Recognition captions.
\item Created a backbone.js-like framework for the Captions editor.
\item All code was reviewed, perfected, and pushed to production.
\end{tightitemize}

\sectionspace


\runsubsection{Phabricator}
\subtitle{| Open Source Contributor \& Team Leader}

\detail{Jan 2013 – May 2013 | Palo Alto, CA \& Ithaca, NY}
\begin{tightitemize}
\item Phabricator is used daily by Facebook, Dropbox, Quora, Asana and more.
\item I created the Meme generator, the entire Lipsum application, ported Tokens to different apps, fixed many bugs and more in PHP and Shell.
\item Led a team from MIT, Cornell, IC London and UHelsinki for the project.
\end{tightitemize}

\sectionspace


\section{Awards} 

\begin{tabular}{rll}
2014 & top 52/2500 & KPCB Engineering Fellow\\
2014 & 2\textsuperscript{nd} most points & Google Code Jam, Qualification Round\\
2014 & 1\textsuperscript{st}/50 & Microsoft Coding Competition, Cornell\\
2013 & National & Jump Trading Challenge Finalist\\
2013 & 7\textsuperscript{th}/120 & CS 3410 Cache Race Bot Tournament \\
2012 & 2\textsuperscript{nd}/150 & CS 3110 Biannual Intra-Class Bot Tournament \\
2011 & National & Indian National Mathematics Olympiad (INMO) Finalist \\
2010 & National & Comp. Soc. of India's National Programming Contest\\
\end{tabular}

\sectionspace


\section{Societies} 

\begin{tabular}{rll}
2014 & top 12\%ile & Tau Beta Pi Engineering Honor Society\\
2014 & National & The Global Leadership and Education Forum (tGELF)\\
2012 & National & Golden Key International Honor Society\\
2012 & National & National Society of Collegiate Scholars\\
\end{tabular}

\sectionspace


\end{minipage} % The end of the right column


%\newpage % Start a new page

%\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%\section{Example Section}

%\end{minipage} % The end of the left column
%\hfill
%\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%\section{Example Section 2}

%\end{minipage} % The end of the right column


\end{document}
